Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage

### 2022-08-03 paper/paper.tex
tracking merge

\begin{abstract}
In this study, we investigate a UAVs and biped robots team system (URTS) for search and rescue usage. The system architecture of URTS is proposed to illustrate the issues that need to be addressed in URTS and the relationships between them. Then we focus on two issues, local motion planning and tracking control. We discuss the methods of local motion planning for UAV flying behavior and robot walking behavior, and then give the control methods for UAV and robot. The relationship between the two issues, the transformation of the reference trajectory, is also explored in detail. By converting the dynamics model of UAV and robot into a unified agent model, a design method for a $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agent in URTS. A novel smoothing signal model of fault signal is embedded into the linearized system to active FTC through observer estimation. The design of this $H_\infty$ observer-based FTC is transformed into a linear matrix inequality (LMI) -constrained optimization problem by a two-step design procedure. Finally, with the help of MATLAB LMI Toolbox, the tracking problem of UAV and robot in URTS is effectively solved. Simulations are given ...
\end{abstract}

@@

The tracking control is to control an agent to follow a desired trajectory. There are many control strategy for MAS. According to the way of the design of controller, it can be divided into centralized control and decentralized control in control field \cite{8931370}. Centralized control means there exist a powerful central controller in MAS to gather the state information and sent the control command back to each agent to reach a global goal. Due to the powerful nature of the central controller, control commands can be determined well and quickly. But when it fails, the whole system will be completely paralyzed. In contrast, decentralized control means that each agent has its own controller to collect and control the agent's own state information. Under this architecture, although the global goal cannot be achieved, the possibility of paralyzing the entire system due to the failure of the controller is avoided.

Besides, the formation control is also a topic in MAS (cite:formation control). Its purpose is to keep a MAS in a formation while moving. Although formation control provides a simple framework for the control of a large number of agents, considering the complexity of the disaster relief environment, formation will make the application of URTS inflexible. It is because we expect that agents in URTS need to organize multiple teams of different scales and types to deal with multiple tasks of different scales and types in a disaster relief environment. In this situation, it is more reasonable to treat each agent as an independent individual and design an independent trajectory for the agent to follow.

@@

In order to make an behavior, we must design a corresponding motion which is handled by local motion planning. The motion is a desired reference trajectory for an actual mechanical system to follow. Finally, a tracking controller is designed to follow this desired reference trajectory.

The agents overall have the same system architecture in URTS except for some subprocess differences. Followed by the concept in \cite{paden2016survey}, a system architecture for an agent used in search and rescue is proposed as shown in Fig. \ref{fig:sys}. The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents $q_{start}$ and an occupy map $\mathcal{C}$. The visual object recognition block provides distance information and object information through the analysis of sensor information. The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot sees a obstacle and decides to climb through it). The detailed functions of remaining 5 blocks, i.e., Tack Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following sections.

@@

\subsection{Task Allocation}
In the URTS, it can be expected that each agent will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g. moving speed or load capacity) and status (e.g. their own position or the amount of supplies carried), and each task has different characteristics (e.g. Urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which makes us want to find the optimal allocation. This problem is refered as task allocation problem or multi-robot task allocation problem. A problem formulation and problem modeling can be found in \cite{Khamis2015}. Although there are many different problem definitions and many problem models to solve this issue, the common goal is to find a set of task-agent pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned and therefore do not further discuss this issue. In other words, every agent knows a destinition $q_{goal}$ it need to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real search and rescue system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}

@@

According to the way of pathfinding, it can be divided into multi-query planner and single-query planner \cite{elbanhawi2014sampling}. Multi-query planner will first construct a roadmap and then use the graph search method on it to query the best path, such as Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}. Single-query planner will complete pathfinding by constructing and querying simultaneously,
%  i.e., the roadmap will be constructed incrementally and toward the goal, 
such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}. However, the environment is dynamic rather static for URTS so some extra structure need to impose on aforementioned planner. Some common dynamic planner can also be found in \cite{elbanhawi2014sampling}, such like PRM with D* search algorithm, dynamic RRT, and extended RRT. All of the above common roadmap-based planners can be applied to the URTS.

Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to Local Motion Planning block to deal with. The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and the constraints on these behaviors will vary. (e.g., curvature constraints of two behavior: running and walking are expected to be different for robot). In this case, a unified planner will become overly complex and impracticable. For this reason, we divide path planning into three subprocess, i.e., Path Planning, Behavior Layer and Local Motion Planning. Then, the global planner, Path Planning block, will regard agent as a point without kinodynamic constraints. The local planners, Local Motion Planning block, will consider the motion planning of a specific behavior.
% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.

By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or sayed waypoints), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space $\mathcal{C}$. Current configuration is obtained by GPS, inertial measurement unit, or other locating techniques. Goal configuration is obtained by previous block, Task Allocation. Configuration space $\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline. $\mathcal{C}$ is a space contain all possible configuration of agent which composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$. For a simpler explanation of how the URTS works, the following assumption is made.
\begin{assumption}
    The locating ability of the URTS is perfect so every agent can know its current configuration $q_{start}$.
\end{assumption}
\begin{assumption}
    A Task Allocation algorithm is already designed so that every agent can know its goal configuration $q_{goal}$.
\end{assumption}
\begin{assumption}
    The URTS is supposed to have an perfect real-time mapping ability so a real-time configuration space $\mathcal{C}$ can be obtain.
\end{assumption}
\begin{assumption} \label{asm:collision} % UAV do not consider obstacle collisions a little wierd.
    UAVs do not consider obstacle collisions because there are few obstacles in the air. Hence, the path of UAVs can be directly assigned rather found by planner. Robots do not consider obstacle collisions in the direction perpendicular to the ground. 
\end{assumption}
From above assumptions, a path of agent can be expressed as a sequence
\begin{equation}
    (\sigma_n), n\in\mathbb{Z}\cap[1,k_f], \sigma_n\in\mathcal{C}
\end{equation}
where $k_f$ is the time step when reaching goal. Since the path planning is dynamic, $(\sigma_n)$ is composed of multiple segments actually. Let $(\sigma_{k_n})$ be the subsequence of $(\sigma_n)$, where $k_n$ is the time step when a replanning decision is occured. Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$. For agents, the replanning decision can be a goal changing that made by human or Task Allocation. For robot, it can be a collision detecting by a dynamic roadmap-based planner. The results path $(\sigma_n)$ is passed to next block, Behavior Layer.

\subsection{Behavior Layer}
% Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
Path Planning tells agents where to go but not how. Take robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ in real scenario. These behaviors with changing position are called "moving" in this paper. Besides, the agents do not always moving. Somtimes they has to suspend to take a action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls). These behaviors without changing position are called an "action" in this paper. More behaviors can be added so that the agent can have more way to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control. The sequence of these behaviors be expressed as:
\begin{equation}
    (\beta_n), n\in\mathbb{Z}\cap[1,k_f], \beta_n\in\mathcal{B}
\end{equation}
It is to say that the path $(\sigma_n)$ is divided into many segments and each corresponding to a specific behavior. Judging an appropriate behavior according to the current environment will be a rather complicated project, so this article only gives the structure of the behavior set. The set of behavior $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig. \ref{fig:behavior}.

@@

\subsection{Local Motion Planning}
After a specific behavior is determined, the next step is to design a motion to achieve that behavior. Local Motion Planning block is like Path Planning block but its scale is smaller and its resolution and precision must be higher. Collision checking is needed since we consider agent as a point in Path Planning block and it is a real body here. Furthermore, the kinodynamic constraint is handled in this block. Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often the same notion in other literature. Therefore, the output of this block is also a path but with a timescale, i.e., sampling period. This path is often referred as a reference trajectory $r(t)$. $r(t)$ describes the position and orientation that needed to be reach over time by a machine system govern by a dynamic equation. Then, Tracking Control block will track $r(t)$ to really do that behavior. Note that the path and trajectory are distinguished in some literature. Different from path $(\sigma_n)$ (or say $r[k]$), a trajectory $r(t)$ has consider the time in physic world. The flowchart of Local Motion Planning block is shown in Fig. \ref{fig:LocalMotionPlanning}
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.4]{fig/LMP.pdf}\caption{The flowchart of local motion planning. The corresponding motion planning will be executed according to the behavior determined by the behavior layer. The terminator, exception, represents an exceptional condition that performs unconsidered behaviors. The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block. $r[k]$ will convert to reference trajectory $r(t)$, an analog signal, by an A to D convertor.}
    \label{fig:LocalMotionPlanning}
\end{figure*}

@@

\section{system description of UAV-Robot Team System}
In order to design a reference trajectory $r(t)$ for the motion of UAV and robot, their dynamic models must be given first. After the system description of UAV and robot, the motion planning of flying and walking as shown in Fig. \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.4]{fig/FandW.pdf}\caption{The flowchart of Flying and Walking. In both two blocks, a smoothed path is obtained by post-processing first. Then the respective motion of behavior is designed. The final outputs of Flying and Walking are all reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.}
    \label{fig:FandW}
\end{figure*}
Before the discussion of the motion planning of these two behavior, the following assumption is maded.
\textit{
    \begin{assumption} \label{asm:cc again}
        The space between obstacles is large enough to eliminate the need for collision checking again, and the average speed of agents is slow enough to ignore dynamic constraints
    \end{assumption}
}
However, for these two behaviors, there all exists an inevitable kinematic constraint on curvature of local motion. Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem. Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking curvature constraint is relatively insignificant. At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure the error will not causing collision. As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$. The post-process will appear in the begining of motion planning process of these two behaviors as shown in Fig. \ref{fig:FandW}.

@@

Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $(\beta_n)=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density. $(\sigma_n')$ is the position reference path $\begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k]
\end{bmatrix}^T$. Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are considered. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be set since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = \begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k] & \psi_r[k]
\end{bmatrix}^T$. The flowchart is shown in Fig. \ref{fig:FandW}.

@@

\textit{
    \begin{remark}
        A frame in $\mathbb{R}^3$ can be determined by given the "position" and "orientation" with respect to a reference frame. That is, given the position and orientation of two joints in a link with known kinematics, the position and orientation of joints between them can be found by IK. Hence, we need to find the  position path and orientation path, which compose the desired path.
    \end{remark}
}

@@

To obtain CoM postion path $(CP_n)$, ZMP path need to obtain first. ZMP path can be obtained through foothold paths $(\sigma^{4}_{k_n})$ and $(\sigma^{5}_{k_n})$ since ZMP needs to lie in the support face and the foothold path point out when a feet is stand on the ground. Suppose the CoM height $z_c$ of robot is constant when walking, then the robot model can be regarded as an 3D-LIPM:
\begin{equation} \label{eq:LIPM}
    \begin{split}
        & \ddot{x} = \frac{g}{z_c}(x - p_x) \\
        & \ddot{y} = \frac{g}{z_c}(y - p_y)
    \end{split}
\end{equation}
where $(x,y)$ is the position of CoM of the inverted pendulum, $g$ is the gravity acceleration, and $(p_x,p_y)$ is the position of ZMP. Since $z_c$, $g$ and $(p_x,p_y)$ are given, $(x,y)$ can be solved. To solve the ODE in (\ref{eq:LIPM}), a method is proposed to convert it to a servo problem \cite{1241826}:
\begin{equation} \label{eq:output tracking}
    \begin{split}
        & \dot{\bar{x}} = A\bar{x} + Bu \\
        & p_x = C\bar{x}
    \end{split}
\end{equation}
where $\bar{x} = \begin{bmatrix}
    x \\ \dot{x} \\ \ddot{x}
\end{bmatrix}$, $A = \begin{bmatrix}
    0 & 1 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0
\end{bmatrix}$, $B = \begin{bmatrix}
    0 \\ 0 \\ 1
\end{bmatrix}$, and $C = \begin{bmatrix}
    1 & 0 & -z_c/g
\end{bmatrix}$. Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference trajectory so that the solution of ODE $x$ in (\ref{eq:LIPM}), i.e., the CoM position path we want is found. Unlike conventional methods, the problem is solved by optimal control. The system is discretized first and the discrete LQ tracker is employed to achieve the output tracking. The formulation can be found in TABLE 4.4-1 in \cite{lewis2012optimal}. The $y$-direction can be found by same procedure since the dynamic of 3D-LIPM in the $x$-direction and $y$-direction is decoupled with same form. The CoM position path $(CP_n)$ then be obtained by combining $x$, $y$ and $z_c$.
% $\bar{x}$ in (\ref{eq:output tracking}),

@@

    \int_{0}^{t}e(\tau)d\tau & e(t) & \dot{e}(t)
\end{bmatrix}\in\mathbb{R}^{3n}$ be the PID tracking error, (\ref{eq:error, state eq}) can be rewrited as:

@@

\begin{equation} \label{eq:7}

@@

\end{bmatrix}^T$, and $A_i=[a_{j,k}]\otimes I_{n}$. Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:7})

@@

\end{bmatrix}\otimes I_{n}$. Sub. (\ref{eq:7}) and (\ref{eq:8}) into (\ref{eq:error}), we get:

@@

where $t_f$ is the final time, $Q \leq 0$ is the weighting matrix of state and estimation error, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated. If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on tracking and estimation error $\tilde{x}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy. Before analyzing the $H_\infty$ observer-based stablized control problem in (\ref{Hinf}), the following lemmas are given:

>>>>

\begin{abstract}
In this study, we investigate a UAVs and biped robots team system (URTS) for search and rescue usage. The system architecture of URTS is proposed to illustrate the issues need to be addressed in URTS and the relationships between them. Then we focus on two issues, local motion planning and tracking control. We discuss the methods of local motion planning for UAV flying behavior and robot walking behavior, and then give the control methods for UAV and robot. The relationship between the two issues, the transformation of the reference trajectory, is also explored in detail. By converting the dynamics model of UAV and robot into a unified agent model, a design method for a $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agent in URTS. A novel smoothing signal model of fault signal is embedded into the linearized system to active FTC through observer estimation. The design of this $H_\infty$ observer-based FTC is transformed into a linear matrix inequality (LMI) -constrained optimization problem by a two-step design procedure. Finally, with the help of MATLAB LMI Toolbox, the tracking problem of UAV and robot in URTS is effectively solved. Simulations are given ...
\end{abstract}

@@

The tracking control is to control an agent to follow a desired trajectory. There are many control strategies for MAS. According to the way of the design of controller, it can be divided into centralized control and decentralized control in control field \cite{8931370}. Centralized control means there exist a powerful central controller in MAS to gather the state information and send the control command back to each agent to reach a global goal. Due to the powerful nature of the central controller, control commands can be determined well and quickly. But when it fails, the whole system will be completely paralyzed. In contrast, decentralized control means that each agent has its own controller to collect and control the agent's own state information. Under this architecture, although the global goal cannot be achieved, the possibility of paralyzing the entire system due to the failure of the controller is avoided.

Besides, the formation control is also a topic in MAS (cite:formation control). Its purpose is to keep a MAS in a formation while moving. Although formation control provides a simple framework for the control of a large number of agents, considering the complexity of the disaster relief environment, formation will make the application of URTS inflexible. It is because we expect that agents in URTS need to organize multiple teams of different scales and types to deal with multiple tasks of different scales and types in a disaster relief environment. In this situation, it is more reasonable to treat each agent as an independent individual and specify an independent trajectory for the agent to follow.

@@

In order to make a behavior, we must design a corresponding motion which is handled by local motion planning. The motion is a desired reference trajectory for an actual mechanical system to follow. Finally, a tracking controller is designed to follow this desired reference trajectory.

The agents overall have the same system architecture in URTS except for some subprocess differences. Followed by the concept in \cite{paden2016survey}, a system architecture for an agent used in search and rescue is proposed as shown in Fig. \ref{fig:sys}. The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents $q_{start}$ and an occupy map $\mathcal{C}$. The visual object recognition block provides distance information and object information through the analysis of sensor information. The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see a obstacle and decides to climb through it). The detailed functions of remaining 5 blocks, i.e., Tack Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following sections.

@@

\subsection{Task Allocation}
In the URTS, it can be expected that each agent will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g. moving speed or load capacity) and status (e.g. their own position or the amount of supplies carried), and each task has different characteristics (e.g. Urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us want to find the optimal allocation. This problem is refered as a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{Khamis2015}. Although there are many different formulations and models to solve the task allocation problem, the common goal is to find a set of task-agent pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned and therefore do not further discuss this issue. In other words, every agent knows a destinition $q_{goal}$ it needs to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real search and rescue system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}

@@

According to the way of pathfinding, it can be divided into multi-query planner and single-query planner \cite{elbanhawi2014sampling}. Multi-query planner will first construct a roadmap and then use the graph search method on it to query the best path, such as Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}. Single-query planner will complete the pathfinding by constructing and querying simultaneously,
%  i.e., the roadmap will be constructed incrementally and toward the goal, 
such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}. However, the environment is dynamic rather static for URTS so some extra structures need to impose on the aforementioned planner. Some common dynamic planners can also be found in \cite{elbanhawi2014sampling}, such like PRM with D* search algorithm, dynamic RRT, and extended RRT. All of the above common roadmap-based planners can be applied to the URTS.

Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to Local Motion Planning block to deal with. The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and the constraints on these behaviors will vary. (e.g., curvature constraints of two behavior: running and walking are expected to be different for robot). In this case, a unified planner will become overly complex and impracticable. For this reason, we divide path planning into three subprocesses, i.e., Path Planning, Behavior Layer and Local Motion Planning. Then, the global planner, Path Planning block, will regard an agent as a point without kinodynamic constraints. The local planners, Local Motion Planning block, will consider the motion planning of a specific behavior.
% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.

By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or sayed waypoints), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space $\mathcal{C}$. Current configuration is obtained by GPS, inertial measurement unit, or other locating techniques. Goal configuration is obtained by the previous block, Task Allocation. Configuration space $\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline. $\mathcal{C}$ is a space contain all possible configurations of agents which are composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$. For a simpler explanation of how the URTS works, the following assumption is made.
\begin{assumption}
    The locating ability of the URTS is perfect so every agent can know its current configuration $q_{start}$.
\end{assumption}
\begin{assumption}
    A Task Allocation algorithm is already designed so that every agent can know its goal configuration $q_{goal}$.
\end{assumption}
\begin{assumption}
    The URTS is supposed to have a perfect real-time mapping ability so a real-time configuration space $\mathcal{C}$ can be obtained.
\end{assumption}
\begin{assumption} \label{asm:collision} % UAV do not consider obstacle collisions a little wierd.
    UAVs do not consider obstacle collisions because there are few obstacles in the air. Hence, the path of UAVs can be directly assigned rather than found by planner. Robots do not consider obstacle collisions in the direction perpendicular to the ground. 
\end{assumption}
From above assumptions, a path of agent can be expressed as a sequence
\begin{equation}
    (\sigma_n), n\in\mathbb{Z}\cap[1,k_f], \sigma_n\in\mathcal{C}
\end{equation}
where $k_f$ is the time step when reaching goal. Since the path planning is dynamic, $(\sigma_n)$ is composed of multiple segments actually. Let $(\sigma_{k_n})$ be the subsequence of $(\sigma_n)$, where $k_n$ is the time step when a replanning decision is occured. Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$. For agents, the replanning decision can be a goal changing that is made by human or Task Allocation. For robot, it can be a collision detecting by a dynamic roadmap-based planner. The results path $(\sigma_n)$ is passed to the next block, Behavior Layer.

\subsection{Behavior Layer}
% Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
Path Planning tells agents where to go but not how. Take robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ in real scenario. These behaviors with changing position are called "moving" in this paper. Besides, the agents do not always moving. Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls). These behaviors without changing position are called an "action" in this paper. More behaviors can be added so that the agent can have more ways to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control. The sequence of these behaviors be expressed as:
\begin{equation}
    (\beta_n), n\in\mathbb{Z}\cap[1,k_f], \beta_n\in\mathcal{B}
\end{equation}
It is to say that the path $(\sigma_n)$ is divided into many segments and each corresponding to a specific behavior. Judging an appropriate behavior according to the current environment will be a rather complicated project, so this article only gives the structure of the behavior set. The set of behavior $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig. \ref{fig:behavior}.

@@

\subsection{Local Motion Planning}
After a specific behavior is determined, the next step is to design a motion to achieve that behavior. Local Motion Planning block is like Path Planning block but its scale is smaller and its resolution and precision must be higher. Collision checking is needed since we consider agent as a point in Path Planning block and it is a real body here. Furthermore, the kinodynamic constraint is handled in this block. Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature. Therefore, the output of this block is also a path but with a timescale, i.e., sampling period. This path is often referred as a reference trajectory $r(t)$. $r(t)$ describes the position and orientation that need to be reach over time by a machine system governed by a dynamic equation. Then, Tracking Control block will track $r(t)$ to really do that behavior. Note that the path and trajectory are distinguished in some literature. Different from path $(\sigma_n)$ (or say $r[k]$), a trajectory $r(t)$ has considered the time in physic world. The flowchart of Local Motion Planning block is shown in Fig. \ref{fig:LocalMotionPlanning}
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.4]{fig/LMP.pdf}\caption{The flowchart of local motion planning. The corresponding motion planning will be executed according to the behavior determined by the behavior layer. The terminator, exception, represents an exceptional condition that performs unconsidered behaviors. The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block. $r[k]$ will convert to reference trajectory $r(t)$, an analog signal, by an A to D convertor.}
    \label{fig:LocalMotionPlanning}
\end{figure*}

@@

\section{system description of UAV-Robot Team System}
In order to design a reference trajectory $r(t)$ for the motion of UAV and robot, their dynamic models must be given first. After the system description of UAV and robot, the motion planning of flying and walking as shown in Fig. \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.4]{fig/FandW.pdf}\caption{The flowchart of Flying and Walking. In both two blocks, a smoothed path is obtained by post-processing first. Then the respective motion of behavior is designed. The final outputs of Flying and Walking are all reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.}
    \label{fig:FandW}
\end{figure*}
Before the discussion of the motion planning of these two behavior, the following assumption is maded.
\textit{
    \begin{assumption} \label{asm:cc again}
        The space between obstacles is large enough to eliminate the need for collision checking again, and the average speed of agents is slow enough to ignore dynamic constraints
    \end{assumption}
}
However, for these two behaviors, there all exist an inevitable kinematic constraint on curvature of local motion. Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem. Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking curvature constraint is relatively insignificant. At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure the error will not cause collision. As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$. The post-process will appear in the begining of motion planning process of these two behaviors as shown in Fig. \ref{fig:FandW}.

@@

Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $(\beta_n)=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density. $(\sigma_n')$ is the position reference path $\begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k]
\end{bmatrix}^T$. Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are considered. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be set beforehand since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = \begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k] & \psi_r[k]
\end{bmatrix}^T$. The flowchart is shown in Fig. \ref{fig:FandW}.

@@

\textit{
    \begin{remark}
        A frame in $\mathbb{R}^3$ can be determined by giving the "position" and "orientation" with respect to a reference frame. That is, given the position and orientation of two joints in a link with known kinematics, the position and orientation of joints between them can be found by IK. Hence, we need to find the  position path and orientation path, which compose the desired path.
    \end{remark}
}

@@

To obtain CoM postion path $(CP_n)$, ZMP path needs to be obtained first. ZMP path can be obtained through foothold paths $(\sigma^{4}_{k_n})$ and $(\sigma^{5}_{k_n})$ since ZMP needs to lie in the support face and the foothold path points out when the feet are on the ground. Suppose the CoM height $z_c$ of robot is constant when walking, then the robot model can be regarded as an 3D-LIPM:
\begin{equation} \label{eq:LIPM}
    \begin{split}
        & \ddot{x} = \frac{g}{z_c}(x - p_x) \\
        & \ddot{y} = \frac{g}{z_c}(y - p_y)
    \end{split}
\end{equation}
where $(x,y)$ is the position of CoM of the inverted pendulum, $g$ is the gravity acceleration, and $(p_x,p_y)$ is the position of ZMP. Since $z_c$, $g$ and $(p_x,p_y)$ are given, $(x,y)$ can be solved. To solve the ODE in (\ref{eq:LIPM}), a method is proposed to convert it to a servo problem \cite{1241826}:
\begin{equation} \label{eq:output tracking}
    \begin{split}
        & \dot{\bar{x}} = A\bar{x} + Bu \\
        & p_x = C\bar{x}
    \end{split}
\end{equation}
where $\bar{x} = \begin{bmatrix}
    x \\ \dot{x} \\ \ddot{x}
\end{bmatrix}$, $A = \begin{bmatrix}
    0 & 1 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0
\end{bmatrix}$, $B = \begin{bmatrix}
    0 \\ 0 \\ 1
\end{bmatrix}$, and $C = \begin{bmatrix}
    1 & 0 & -z_c/g
\end{bmatrix}$. Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference trajectory so that the solution $x$ of ODE in (\ref{eq:LIPM}) can be obtained, i.e., the CoM position path we want is found. Unlike conventional methods, the problem is solved by the optimal control. The system is discretized first and the discrete LQ tracker is employed to achieve the output tracking. The formulation can be found in TABLE 4.4-1 in \cite{lewis2012optimal}. The $y$-direction can be found by same procedure since the dynamic of 3D-LIPM in the $x$-direction and $y$-direction is decoupled with same form. The CoM position path $(CP_n)$ then be obtained by combining $x$, $y$ and $z_c$.
% $\bar{x}$ in (\ref{eq:output tracking}),

@@

    \int_{0}^{t}e^T(\tau)d\tau & e^T(t) & \dot{e}^T(t)
\end{bmatrix}^T\in\mathbb{R}^{3n}$ be the PID tracking error, (\ref{eq:error, state eq}) can be rewrited as:

@@

\begin{equation} \label{eq:smooth model}

@@

\end{bmatrix}^T$, and $A_i=[a_{j,k}]\otimes I_{n}$. Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:smooth model})

@@

\end{bmatrix}\otimes I_{n}$. Sub. (\ref{eq:smooth model}) and (\ref{eq:8}) into (\ref{eq:error}), we get:

@@

where $t_f$ is the final time, $Q \geq 0$ is the weighting matrix of state and estimation error, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated. If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on tracking and estimation error $\tilde{x}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy. Before analyzing the $H_\infty$ observer-based stablized control problem in (\ref{Hinf}), the following lemmas are given:
